% Journal:
%   Journal of Ambient Intelligence and Smart Environments (JAISE), IOS Press
%   Web Intelligence and Agent Systems: An International Journal (wias)
%   Semantic Web: Interoperability, Usability, Applicability (SW)
% Latex 2e
% Test file iosart2c.tex

%[seceqn,secfloat,secthm,crcready]

% options: wias, jaise, sw
\documentclass{iosart2c}


\usepackage[T1]{fontenc}
\usepackage{times}%

\usepackage{natbib}
%\usepackage[dvips]{hyperref}
\usepackage{amsmath}
\usepackage{dcolumn}
%\usepackage{endnotes}
\usepackage{graphics}


\newcolumntype{d}[1]{D{.}{.}{#1}}


\firstpage{1} \lastpage{5} \volume{1} \pubyear{2009}


\begin{document}
\begin{frontmatter}                           % The preamble begins here.

%
%\pretitle{Pretitle}
\title{MLODE paper \thanks{Footnote in title.}}

\runningtitle{MLODE paper}
%\subtitle{Subtitle}

%\review{Name Surname, University, Country}{Name Surname, University, Country}{Name Surname, University, Country}


\author[A]{\fnms{Steven} \snm{Moran}\thanks{Corresponding author. E-mail: editorial@iospress.nl.}\thanks{Do not use capitals for the author's surname.}},
\author[B]{\fnms{Richard} \snm{Littauer}}
and
\author[C]{\fnms{Boris} \snm{Villazon-Terrazas}}
\runningauthor{Moran, Littauer and Villazon-Terrazas}
\address[A]{Journal Production Department, IOS Press, Nieuwe Hemweg 6b, 1013 BG, Amsterdam,\\ The Netherlands\\
E-mail: first@somewhere.com}
\address[B]{Department first, then University or Company name, Insert a complete correspondence (mailing) address,
Abbreviate US states, Include country\\
E-mail: \{second,third\}@somewhere.com}
\address[C]{Intelligent Software Components, iSOCO, S.A., Av. del Partenon 16-18, Madrid, Spain\\
E-mail: \{bvillazon\}@isoco.com}

\begin{abstract}
The abstract should be clear, descriptive, self-explanatory and no longer than 200 words. It should also
be suitable for publication in abstracting services. Do not include references or formulae in the abstract.
\end{abstract}

\begin{keyword}
Keyword one\sep keyword two\sep keyword three\sep keyword four\sep keyword five
\end{keyword}

\end{frontmatter}


\section{Introduction}
\input{introduction}

\section{Related Work}
\input{relatedwork}

\section{Language resources with geospatial information}
\input{langeo}

\section{Conclusions}
\input{conclusions}

\end{document}
